---
title: "README"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

For the future, I intend for this package to contain functions that I use to create plots.

At the moment, there's just `theme_carly_presents()`, which simplifies `ggplot2::theme_bw()` a bit for a low-resolution format like presentations. I'mm just testing it as a proof of concept. You can see [an example](https://speakerdeck.com/carlislerainey/ggcarly-theme-carly-presents) I put on SpeakerDeck. I also added several examples below.

# Installation

```
devtools::install_github("carlislerainey/ggcarly")
```

# Examples

## Latent Dissent

```{r latent-dissent, fig.height=4, fig.path="figs/", fig.width=8, message=FALSE}
# load packages
library(tidyverse)
library(ggcarly)

# load latent dissent data
dissent_df <- read_csv("https://raw.githubusercontent.com/carlislerainey/latent-dissent/master/latent-dissent.csv") %>% 
  glimpse()

# plot eta
p <- ggplot(dissent_df, aes(x = year, y = eta, group = ccode)) + 
  geom_line(alpha = 0.2) + 
  geom_line(data = filter(dissent_df, country_name %in% c("United States", "Canada", "Mexico", "Russia")),
              aes(x = year, y = eta, color = country_name), alpha = 1, size = 2) + 
  scale_color_brewer(type = "qual", palette = 2) + 
  labs(title = "A Latent Measure of Dissent",
       x = "Year",
       y = "Dissent",
       color = "Country")

# default theme
p

# bw theme
p + theme_bw()

# minimal theme
p + theme_minimal()

# carly_presents
p + theme_carly_presents()

```

## Scatterplot

```{r scatterplot, fig.height=3.5, fig.path="figs/", fig.width=8}
# load packages
library(ggplot2)
library(ggcarly)

# scatterplot
ggplot(mtcars, aes(wt, mpg, size = hp)) + 
  geom_point(shape = 21) + 
  labs(x = "Weight (1000 lbs.)",
       y = "Miles Per Gallon",
       size = "Gross Horsepower") + 
  theme_carly_presents()
```

## Bar Plot

```{r bar-plot, fig.height=3.5, fig.path="figs/", fig.width=6}
# load packages
library(ggplot2)
library(ggcarly)

# barplot
ggplot(mpg, aes(class)) + 
  geom_bar() + 
  coord_flip() + 
  theme_carly_presents()
```

## Facetted Scatterplot

```{r facetted-scatterplot, fig.height=7, fig.path="figs/", fig.width=8}
# load packages
library(ggplot2)
library(ggcarly)

# facetted scatterplot
ggplot(mpg, aes(displ, hwy)) + 
  geom_point() + 
  facet_wrap(vars(class)) + 
  theme_carly_presents()
```

## Histogram

```{r histogram, fig.height=3, fig.path="figs/", fig.width=4}
# load packages
library(ggplot2)
library(ggcarly)

# dotplot
ggplot(mtcars, aes(x = mpg)) + 
  geom_histogram(bins = 10) + 
  theme_carly_presents()
```

## Dot-and-Box Plot

Example from [here](http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html#Dot%20+%20Box%20Plot).

```{r dot-and-box-plot, fig.height=5, fig.path="figs/", fig.width=8}
# load packages
library(ggplot2)
library(ggcarly)

# dot-and-box plot
g <- ggplot(mpg, aes(manufacturer, cty))
g + geom_boxplot() + 
  geom_dotplot(binaxis='y', 
               stackdir='center', 
               dotsize = .5, 
               fill="red") +
  theme(axis.text.x = element_text(angle=65, vjust=0.6)) + 
  labs(title="Box plot + Dot plot", 
       subtitle="City Mileage vs Class: Each dot represents 1 row in source data",
       caption="Source: mpg",
       x="Class of Vehicle",
       y="City Mileage") + 
  theme_carly_presents() + 
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust = 1))
```
